# Measuring Balance

```{r include=F}
source(here::here("code/analysis/load.R"))
main <- sources %>%
    calculate_balance(
        types = c("org_category", "cfscore"),
    )
main.i2 <- sources %>%
    calculate_balance(
        types = c("org_category", "cfscore"),
        cfscore.options = list(impute.all=T)
    )
knitr::opts_chunk$set(fig.height = 4)
```

This document contains analysis related to the measure of balance/bothsides journalism.

- Many different possible interpretations, but we focus on the idea of "both sides" journalism/"equal coverage"
- We define balance as an **article level indicator** that captures whether an article contains a quote from **both** a liberal and conservative source 
    - We assume that the source of the quote is a good proxy for its content
- "Left leaning" source: `environmental_advocacy` classification OR `cfscore < -0.3`
    - NRDC, Environmental Defense Fund, Sierra Club
- "Right leaning" source: `fossil_fuel_interest` classification OR `cfscore > 0.3`
    - American Petroleum Institute, Exxon Mobile, US Chamber of Commerce
- Balance Dummy: article includes both a "right" and "left" source
    - `r round(sum(main$balance, na.rm=T) * 100/nrow(main))`% of articles are "balanced" by this definition

## Alternative Measures of Balance

- Here, I show that our measure of balance is correlated with other reasonable measures
- Balance indicator correlated with mean ideology score closer to 0
- Balance indicator correlated with higher source ideology SD
- Balance indicator correlated with lower normalized absolute difference between number of left and right sources

### Histograms

```{r, fig.width=12}
ggarrange(plotlist = list(
    ggplot(main, aes(x = cfscore, fill = balance)) +
        geom_histogram() +
        theme_min,
    ggplot(main, aes(x = cfscore.sd, fill = balance)) +
        geom_histogram() +
        theme_min,
    ggplot(main, aes(x = diff_normalized, fill = balance)) +
        geom_histogram() +
        theme_min
), common.legend = T, legend = "bottom", nrow = 1)
ggsave(here("paper/figures/balance-cf-hists.png"), width = 8, height = 4)
```

### Scatter 

```{r}
ggplot(main, aes(x = cfscore, y = cfscore.sd, color = balance)) +
    geom_point(alpha = 0.3, stroke = NA) +
    theme_min
ggsave(here("paper/figures/balance-cfscoresd-scatter.png"), width = 6, height = 4)
```

### Regressions

```{r}
ms <- list(
    feols(balance ~ cfscore, data = main),
    feols(balance ~ cfscore | year + source, data = main),
    feols(balance ~ cfscore.sd, data = main),
    feols(balance ~ cfscore.sd | year + source, data = main),
    feols(balance ~ diff_normalized, data = main),
    feols(balance ~ diff_normalized | year + source, data = main)
)
etable2(ms, here("paper/tables/balance-cf-regressions.tex"))
```

## Balance trend over time

- Balance generally declining over time
- Particular drop in 2017-2020

```{r}
plots <- list(
    main %>% group_by(year) %>% balance_rate() %>%
        ggplot(aes(x = year, y = as.numeric(balance))) +
        geom_line() +
        theme_min +
        scale_x_continuous(breaks = seq(2012, 2022, 2)) +
        labs(y = "Balance", x = "Year"),
    main %>% group_by(year) %>% summarize(cfscore.sd = mean(cfscore.sd, na.rm = T)) %>% ggplot(aes(x = year, y = cfscore.sd)) +
        geom_line() +
        theme_min +
        scale_x_continuous(breaks = seq(2012, 2022, 2)) +
        labs(y = "Cfscore SD", x = "Year")
)
ggarrange(plotlist = plots)
ggsave(here("paper/figures/balance-overview-year.png"), width = 6, height = 4)
```

### Regression

- 5.6% less balanced articles in Trump era

```{r}
ms <- list(
    feols(balance ~ year, data=main),
    feols(balance ~ admin, data=main),
    feols(balance ~ year, data=main.i2),
    feols(balance ~ admin, data=main.i2)
)
etable2(ms, here('paper/tables/balance-overview.tex'))
```


### Robust to imputation strategy

- Our main specification uses matched DIME cfscore and includes imputed cfscores when data is missing.
- Also, we count environmental_advocacy as left and fossil fuel categorization as right no matter what.
- We can look at the balance over time varying this specification:
    - Category only
    - CFscore only
    - No imputation
    - All imputation
- If anything the other specifications make the negative trend more pronounced

```{r}
specs <- list(
    list("types" = c("org_category"), cfscore.options = list(), label = "Category only"),
    list("types" = c("cfscore"), cfscore.options = list(), label = "Cfscore only"),
    list("types" = c("org_category", "cfscore"), cfscore.options = list(impute.off = T, nwd.sd.thres = 0.8), label = "Category + raw cfscore"),
    list("types" = c("org_category", "cfscore"), cfscore.options = list(nwd.sd.thresh = 0.8), label = "Category + imputed cfscore"),
    list("types" = c("org_category", "cfscore"), cfscore.options = list(impute.all = T, nwd.sd.thresh = 0.8), label = "Category + total imputation")
)
df <- lapply(specs, \(t) {
    sources %>%
        calculate_balance(
            types = t$types,
            cfscore.options = t$cfscore.options,
        ) %>%
        mutate(label = t$label)
}) %>% bind_rows()
df %>% ggplot(aes(x = date, y = as.numeric(balance), color = label)) +
    geom_smooth(se = F) +
    theme_min +
    labs(x = "Date", y = "Balance", color = "Specification")
ggsave(here("paper/figures/balance-overview-robust-1.png"), width = 6, height = 4)
df %>%
    group_by(year, label) %>%
    balance_rate() %>%
    ggplot(aes(x = year, y = balance, color = label)) +
    geom_line() +
    theme_min +
    labs(x = "Date", y = "Balance", color = "Specification")
```

### Robustness to bad match threshold

- When we match to DIME, we have to make a decision about what to do when there are multiple matches with a wide range of cfscores. 
- Our default specification throws out matches with SD > 0.5 and uses the imputed score instead. 
- We can vary the threshold used
- The negative time trend is increasingly apparent the more strictly we reject bad matches.

```{r}
df <- lapply(seq(0.1, 1, 0.1), \(x) {
    sources %>%
        calculate_balance(
            types = c("org_category", "cfscore"),
            cfscore.options = list(nwd.sd.thresh = x),
        ) %>%
        mutate(label = x)
}) %>% bind_rows()
df %>% ggplot(aes(x = date, y = as.numeric(balance), color = as.factor(label))) +
    geom_smooth(se = F) +
    theme_min +
    labs(x = "Date", y = "Balance", color = "Specification")
ggsave(here("paper/figures/balance-overview-robust-2.png"), width = 6, height = 4)
```

### Robustness to varying left/right threshold

- Our measure of balance depends on an arbitrary threshold 't'
- Organizations with cfscore > t and cfscore < -t are classified as "right" and "left"
- Our main specification uses t=0.3 
- Vary `t` and observe similar time trends

```{r}
seq(0.1, 0.6, 0.1) %>%
    lapply(\(t) {
        sources %>%
            group_by(textfile, date) %>%
            calculate_balance(
                types = c("org_category", "cfscore"),
                cfscore.options = list(nwd.sd.thresh = 0.8),
                thresh = t
            ) %>%
            mutate(thresh = t)
    }) %>%
    bind_rows() %>%
    ggplot(aes(x = date, y = as.numeric(balance), color = as.factor(thresh))) +
    geom_smooth(se = F) +
    theme_min +
    labs(x = "Date", y = "Balance", color = "Threshold")
ggsave(here("paper/figures/balance-overview-robust-3.png"), width = 6, height = 4)
```

## Variation by Newspaper

- How much do newspapers vary in their level of balance
- WSJ is more balanced likely because it focuses on business audience
- NYT does not drop balance as much as other sources
- Overall, there is some outlet level variation. But also, lots of variation unexplained by outlet


### Smoothed Trend

```{r}
ggarrange(plotlist = list(
    main %>% ggplot(aes(x = date, y = as.numeric(balance), color = source)) +
        geom_smooth(method = "loess", se = F) +
        labs(y = "Balance", x = "Date", color = "Newspaper") +
        theme_min,
    main %>% ggplot(aes(x = date, y = as.numeric(cfscore.sd), color = source)) +
        geom_smooth(method = "loess", se = F) +
        labs(y = "Source SD", x = "Date", color = "Newspaper") +
        theme_min
), common.legend = T, legend = "bottom")
```

### Mean Balance By Year

```{r}
main %>%
    group_by(year, source) %>%
    summarize(balance = sum(balance, na.rm = T) / sum(!is.na(balance))) %>%
    ggplot(aes(x = year, y = as.numeric(balance), color = source, lty = source, shape = source)) +
    geom_line() +
    geom_point() +
    theme_min +
    scale_x_continuous(breaks = seq(2012, 2022, 2)) +
    labs(y = "Balance", x = "Date")
ggsave(here("paper/figures/balance-overview-outlet.png"), width = 6, height = 4)
```

### Group by Newspaper Lean

- WSJ is the only "right leaning newspaper"
- NYT, LAT, WAPO "left"
- USAToday, ChicagoT, "center"

```{r}
main$newspaper_lean <- replace_na(main$newspaper_lean, "CENTER")
main %>%
    group_by(year, newspaper_lean) %>%
    summarize(balance = sum(balance, na.rm = T) / sum(!is.na(balance))) %>%
    ggplot(aes(x = year, y = as.numeric(balance), color = newspaper_lean)) +
    geom_line() +
    geom_point() +
    theme_min +
    scale_x_continuous(breaks = seq(2012, 2022, 2)) +
    scale_color_manual(values=c('CENTER' = 'grey40', 'LEFT'='dodgerblue', 'RIGHT'='coral')) + 
    labs(y = "Balance", x = "Date")
```

### Regressions

```{r}
ms <- list(
    feols(balance ~ source, data = main),
    feols(balance ~ source * year, data = main),
    feols(balance ~ source | year, data = main)
)
etable2(ms, here("paper/tables/source-balance.tex"))
ms2 <- list(
    feols(balance ~ (newspaper_lean == "RIGHT") * post2016, data = main),
    feols(balance ~ (newspaper_lean == "RIGHT") * post2016 | year + source, data = main)
)
etable2(ms, here("paper/tables/source-lean-balance.tex"))
```

## Conclusions

- We show balance in coverage as defined by types and ideology of cited organizations is lower during 2016-2020
    - For some specifications, the overall trend is negative even into the Biden admin
    - The outlet level analysis suggests that WSJ is somewhat different and continued to cite business sources, while left and center declined after 2016
    - This doesn't survive the basic TWFE specification, although the estimate is the same magnitude
- Lots of variation unexplained by outlet and year level factors. Is low R2 the best way to understand this?

## Appendix / Supplementary


### Mean Slant over Time
```{r}
main %>%
    ggplot(aes(x = date, y = cfscore)) +
    geom_smooth(method = "loess") +
    labs(
        y = "Mean Slant (cfscore)",
        x = "Date"
    ) +
    theme_min
ggsave(here("paper/figures/slant-overview.png"), width = 6, height = 4)
```

### Balance/Slant Scatter Plot
```{r}
main %>%
    filter(!is.na(balance)) %>%
    ggplot(aes(x = date, y = cfscore, color = balance, stroke = NA)) +
    geom_hline(yintercept = 0, lty = 2) +
    geom_point(alpha = 0.1, size = 3, position = position_jitter(height = 0.04)) +
    geom_smooth(se = F) +
    labs(y = "Slant (cfscore)", x = "Date", color = "Balance") +
    theme_min
ggsave(here("paper/figures/balance-slant-scatter.png"), width = 6, height = 4)
```

### Including politicians 

```{r}
df <- list(
    c("org_category", "cfscore"),
    c("org_category", "cfscore", "party")
) %>%
    lapply(\(t) {
        sources %>%
            calculate_balance(
                types = t,
            ) %>%
            mutate(types = paste0(t, collapse = ","))
    }) %>%
    bind_rows()
df %>%
    ggplot(aes(x = date, y = as.numeric(balance), color = as.factor(types))) +
    geom_smooth(se = F) +
    theme_min +
    labs(x = "Date", y = "Balance", color = "Threshold")
```

#### Politicians and SD

Interesting pattern with SD. Parabolic shape...

```{r}
specs <- list(
    list("types" = c("org_category", "cfscore"), cfscore.options = list(nwd.sd.thresh = 0.8), label = "Default"),
    list("types" = c("org_category", "cfscore"), cfscore.options = list(nwd.sd.thres = 0.8, pols = T), label = "Include Politician CFscore")
)
df <- specs %>%
    lapply(\(t) {
        sources %>%
            calculate_balance(
                types = t$types,
                cfscore.options = t$cfscore.options,
            ) %>%
            mutate(label = t$label)
    }) %>%
    bind_rows()
df %>% ggplot(aes(x = date, y = as.numeric(cfscore.sd), color = label)) +
    geom_smooth(method = "loess") +
    theme_min +
    labs(x = "Date", y = "SD", color = "model")
```