---
title: News Sources, Journalists and Climate Change 
author: Sylvan Zheng 
output:
    html_document:
        toc: true
---

```{r include=F}
source(here::here("code/analysis/load.R"))
```

# Basic Descriptives
## Ns

```{r}
nrow(articles)
nrow(sources)
nrow(authors)
```
## Articles

### Number Over Time By outlet

```{r}
articles %>%
    group_by(year, source) %>%
    summarize(n = n()) %>%
    ggplot(aes(x = year, y = n, color = source)) +
    geom_line() +
    theme_bw() +
    scale_x_continuous(breaks = c(2012, 2014, 2016, 2018, 2020, 2022)) +
    labs(
        x = "Year",
        y = "Number of Articles",
        color = "Newspaper"
    ) +
    theme_min
ggsave(here("paper/figures/time_trend_n_articles.png"), width = 6, height = 4)
```

## Sources

### Number per Article
```{r, fig.height=4}
articles$n_srcs %>% hist()
summary(articles$n_srcs)
```

### Number per Article over Time
```{r, fig.height=4}
sources %>%
    group_by(year) %>%
    summarize(n = n(), n_articles = length(unique(filename)), avg_sources = n / n_articles) %>%
    ggplot(aes(x = year, y = avg_sources)) +
    geom_line() +
    scale_x_continuous(breaks = seq(2012, 2022, 2)) +
    theme_min

etable(feols(n_srcs ~ post2016, data = articles)) %>% htmlTable()
```

### Number per Outlet

```{r, fig.height=4}
sources %>%
    group_by(source) %>%
    summarize(n = n(), n_articles = length(unique(filename)), avg_sources = n / n_articles) %>%
    kable()

sources %>%
    group_by(source, year) %>%
    summarize(n = n(), n_articles = length(unique(filename)), avg_sources = n / n_articles) %>%
    ggplot(aes(x = year, y = avg_sources, color = source)) +
    geom_line() +
    theme_min
```

```{r}
# The example articles
# filter(str_detect(filename, "1270322870.xml|1731405273.xml")) %>%
```

### Source Types (Table 1)

```{r}
gen.cats <- table(sources$category) %>%
    prop.table() %>%
    as.data.frame() %>%
    rename(Category = "Var1") %>%
    mutate(
        Freq = paste0(round(100 * Freq, digits = 1), "%")
    )

sources$category2 <- case_when(
    sources$env_category == "environmental" ~ paste(sources$category, "- Environmental"),
    sources$env_category == "fossil fuel" ~ paste(sources$category, "- Fossil Fuel"),
    sources$category == "Politician" & sources$pol_party == "Democrat" ~ "Politician - Democrat",
    sources$category == "Politician" & sources$pol_party == "Republican" ~ "Politician - Republican",
    sources$category == "Politician" & sources$category == "Politician" ~ "Politician - International",
    sources$category == "Citizen" ~ "Other",
    sources$category == "Advocacy" ~ "Advocacy - Other",
    sources$category == "Business" ~ "Business - Other",
    TRUE ~ sources$category
)
sub.cats <- table(sources$category2) %>%
    prop.table() %>%
    as.data.frame() %>%
    rename(Category = "Var1") %>%
    mutate(
        Freq = paste0(round(100 * Freq, digits = 1), "%")
    )

rbind(gen.cats, sub.cats) %>%
    distinct() %>%
    kable()
```

### Distribution of source types by newspaper

```{r}
sources %>%
    mutate(
        category = factor(category, levels = c(
            "Academic",
            "Advocacy",
            "Business",
            "Bureaucrat",
            "Politician",
            "International",
            "Media",
            "Other"
        ))
    ) %>%
    group_by(category, source) %>%
    summarize(n = n()) %>%
    group_by(source) %>%
    mutate(prop = n / sum(n)) %>%
    ungroup() %>%
    ggplot(
        aes(x = reorder(source, n), fill = fct_rev(category), y = prop)
    ) +
    geom_bar(stat = "identity") +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "bottom") +
    labs(x = "", y = "Prop", fill = "Category") +
    scale_fill_brewer(palette = "Set2", direction = -1) +
    coord_flip() +
    guides(fill = guide_legend(reverse = TRUE))
ggsave(here("paper/figures/source-dist.png"), width = 8, height = 6)

sources.s2 <- sources %>%
    mutate(category.slant2 = case_when(
        category.slant %in% c("Bureaucrat", "International", "Politician") ~ "Other",
        category.slant %in% c("Academic", "Media", "Advocacy") ~ "Other",
        TRUE ~ category.slant
    )) %>%
    mutate(
        category.slant2 = factor(category.slant2, levels = c(
            "Environmental",
            "Business",
            "Fossil Fuel",
            "Democrat",
            "Republican",
            "Other"
        ))
    )
sources.s2 %>%
    group_by(category.slant2, source) %>%
    summarize(n = n()) %>%
    group_by(source) %>%
    mutate(prop = n / sum(n)) %>%
    ungroup() %>%
    ggplot(
        aes(x = reorder(source, n), fill = fct_rev(category.slant2), y = prop)
    ) +
    geom_bar(stat = "identity") +
    scale_fill_manual(values = c(
        "Environmental" = "#91bfdb",
        "Democrat" = "#4575b4",
        "Republican" = "#d73027",
        "Fossil Fuel" = "#fc8d59",
        "Business" = "#fee090",
        "Other" = "#ffffbf"
    )) +
    theme_bw() +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "bottom") +
    labs(x = "", y = "Prop", fill = "Category") +
    coord_flip() +
    guides(fill = guide_legend(reverse = TRUE))
ggsave(here("paper/figures/source-dist-2.png"), width = 8, height = 6)

sources.s2$category.slant2 %>%
    table() %>%
    prop.table() %>%
    kable()
```

```{r}
articles$author_name %>% unique %>% length
articles$author_normalized %>% unique %>% length
authors %>% nrow
```


## DIME correlates to category

```{r}
feols(cfscore ~ category.slant, data = sources) %>%
    etable() %>%
    htmlTable()
```

### DIME coverage
```{r}
s <- sources %>% make_cfscore()
n_covered.i <- s %>%
    filter(!is.na(cfscore.org)) %>%
    nrow()
n_orgs.i <- s %>%
    filter(!is.na(cfscore.org)) %>%
    .$org_id %>%
    unique() %>%
    length()
pct.i <- round(n_covered.i / nrow(s) * 100)

s <- sources %>% make_cfscore(list(impute.off = T))
n_covered <- s %>%
    filter(!is.na(cfscore.org)) %>%
    nrow()
n_orgs <- s %>%
    filter(!is.na(cfscore.org)) %>%
    .$org_id %>%
    unique() %>%
    length()
sprintf("We match %s organizations to DIME accounting for %s pct of sources. After imputation, we retrieve scores for %s orgs accounting for %s pct of sources.", 
    n_orgs, 
    n_covered * 100 / nrow(s), n_orgs.i, pct.i)
```



### Top Source DIME scores 

```{r}
dt <- sources %>%
    make_cfscore(list(impute.all = T)) %>%
    filter(!is.na(cfscore.org), !is.na(org_id)) %>%
    group_by(org_id, organization_name, cfscore.org) %>%
    summarize(
        n = n()
    ) %>%
    arrange(desc(n)) %>%
    head(50)
dt %>% ggplot(aes(x = cfscore.org, size = sqrt(n), y = n, color = cfscore.org, label = organization_name)) +
    theme_bw() +
    scale_y_log10() +
    scale_x_continuous(limits = c(-1.5, 1.2)) +
    scale_color_gradient(low = "blue", high = "red") +
    geom_vline(xintercept = 0, lty = "dashed") +
    theme(panel.grid = element_blank(), axis.text.y = element_blank()) +
    labs(x = "DIME Ideology", y = "") +
    geom_text_repel(
        direction = "y",
        min.segment.length = 999
    ) +
    guides(size = "none", color = "none", fill = "none")
ggsave(here("paper/figures/dime-scatter-100.png"), width = 10, height = 6)
```

### Top DIME over time

```{r}
dt7 <- dt %>%
    arrange(desc(n)) %>%
    head(7)
sources %>%
    filter(org_id %in% dt7$org_id) %>%
    group_by(year, organization_name, org_id, cfscore) %>%
    summarize(n = n()) %>%
    ggplot(aes(
        x = year, y = n, color = cfscore < 0, lty = organization_name
    )) +
    geom_smooth(se = F) +
    theme_min
```

### Politicians 

```{r}
pres <- sources %>%
    mutate(
        pres = case_when(
            str_detect(person_name, "Biden") ~ "Biden",
            str_detect(person_name, "Obama") ~ "Obama",
            str_detect(person_name, "Trump") ~ "Trump",
            category.slant %in% c("Democrat", "Republican") ~ category.slant,
            TRUE ~ NA
        )
    )
npy <- sources %>%
    group_by(year) %>%
    summarize(npy = n())

ggarrange(plotlist = list(
    pres %>%
        group_by(year, pres) %>%
        filter(!is.na(pres)) %>%
        summarize(n = n()) %>%
        ggplot(aes(x = year, y = n, color = pres)) +
        geom_line() +
        theme_min,
    # Normalize by # of sources per year...
    pres %>%
        group_by(year, pres) %>%
        filter(!is.na(pres)) %>%
        summarize(n = n()) %>%
        left_join(npy) %>%
        ggplot(aes(x = year, y = n / npy, color = pres, shape = pres)) +
        geom_line() +
        geom_point() +
        scale_x_continuous(breaks = seq(2012, 2022, 4)) +
        theme_min
), common.legend = T, legend = "bottom")
```

## Journalists

### Demographics
```{r}
ggarrange(plotlist = list(
    authors %>% ggplot(aes(x = age_est_2017)) +
        geom_histogram(),
    authors %>% ggplot(aes(x = elite_undergrad_ivyplus)) +
        geom_bar(stat = "count"),
    authors %>% ggplot(aes(x = edu.has_postgrad)) +
        geom_bar(stat = "count"),
    authors %>% ggplot(aes(x = field.journo)) +
        geom_bar(stat = "count"),
    authors %>% ggplot(aes(x = gender)) +
        geom_bar(stat = "count"),
    authors %>% ggplot(aes(x = race.nonwhite)) +
        geom_bar(stat = "count")
))
```

### Demographics over time

Unit of analysis: unique journalists per year

```{r warning=F, message=F}
journo.years <- articles %>%
    group_by(author_name, year, elite_undergrad_ivyplus, edu.undergrad, edu.has_postgrad, is_career, field.journo, age_est, gender, race.nonwhite) %>%
    summarize(n = n()) %>%
    filter(!is.na(author_name))
age.plt <- journo.years %>%
    ggplot(aes(x = year, y = as.numeric(age_est > 37))) +
    geom_smooth(method = "loess") +
    labs(x = "Year", y = "Age > 37")
ivy.plt <- journo.years %>%
    ggplot(aes(x = year, y = as.numeric(elite_undergrad_ivyplus))) +
    geom_smooth(method = "loess") +
    labs(y = "Ivy League", x = "Year")
fj.plt <- journo.years %>%
    ggplot(aes(x = year, y = as.numeric(field.journo))) +
    labs(y = "Journalism Degree", x = "Year") +
    geom_smooth(method = "loess")

pg.plt <- journo.years %>%
    ggplot(aes(x = year, y = as.numeric(edu.has_postgrad))) +
    labs(y = "Postgraduate Degree", x = "Year") +
    geom_smooth(method = "loess")
gender.plt <- journo.years %>%
    ggplot(aes(x = year, y = as.numeric(gender == "female"))) +
    labs(y = "Female", x = "Year") +
    geom_smooth(method = "loess")
race.plt <- journo.years %>%
    ggplot(aes(x = year, y = as.numeric(race.nonwhite))) +
    labs(y = "Nonwhite", x = "Year") +
    geom_smooth(method = "loess")
plts <- list(age.plt, ivy.plt, fj.plt, gender.plt, pg.plt, race.plt) %>%
    lapply(function(p) {
        p +
            theme_bw() +
            theme(panel.grid = element_blank()) +
            scale_x_continuous(breaks = seq(2012, 2022, 2))
    })
ggarrange(plotlist = plts)
ggsave(here("paper/figures/journo-agg-2.png"), width = 10, height = 6)
```

# Ideological Sources


```{r}
sources %>%
    group_by(year, category.slant) %>%
    summarize(n = n()) %>%
    ggplot(aes(x = year, y = n, color = category.slant, lty = category.slant)) +
    geom_smooth(se = F) +
    theme_min

sources_per_year <- sources %>%
    group_by(year) %>%
    summarize(year.n = n())
sources %>%
    group_by(year, category.slant) %>%
    summarize(n = n()) %>%
    left_join(sources_per_year) %>%
    ggplot(aes(x = year, y = n / year.n, color = category.slant, lty = category.slant)) +
    geom_line() +
    theme_min
```

# Coverage/data quality

## Articles with DIME and journalist information

```{r}
articles.b <- sources %>% calculate_balance(types = c("org_category", "cfscore"))
articles.with.author <- articles.b %>% filter(!is.na(author))
articles.with.author.cfscore <- articles.with.author %>% filter(!is.na(cfscore))
nrow(articles.with.author)
nrow(articles.with.author.cfscore)
```

## DIME coverage

```{r}
nrow(sources %>% filter(!is.na(cfscore))) / nrow(sources)

nrow(sources %>% filter(!is.na(cfscore.impute))) / nrow(sources)

table(
    !is.na(sources$cfscore),
    sources$category.slant
)

n_eligible <- sources %>%
    filter(tolower(category.slant) %in% c("advocacy", "environmental", "fossil fuel", "business", "democrat", "republican")) %>%
    nrow()
# Excludes bureaucrat, media, other
nrow(sources %>% filter(!is.na(cfscore))) / n_eligible
nrow(sources %>% filter(!is.na(cfscore.impute))) / n_eligible
```


# Citation Topics are Correlated to Source Types, Politician Parties, Ideology

```{r}
list(
    feols(src_topic == "Business" ~ category.slant, data = sources),
    feols(src_topic == "Environment" ~ category.slant, data = sources),
    feols(src_topic == "Policy" ~ category.slant, data = sources)
) %>%
    etable() %>%
    htmlTable()
list(
    feols(src_topic == "Business" ~ env_category, data = sources),
    feols(src_topic == "Environment" ~ env_category, data = sources),
    feols(src_topic == "Policy" ~ env_category, data = sources)
) %>%
    etable() %>%
    htmlTable()
list(
    feols(src_topic == "Business" ~ pol_party, data = sources),
    feols(src_topic == "Environment" ~ pol_party, data = sources),
    feols(src_topic == "Policy" ~ pol_party, data = sources)
) %>%
    etable() %>%
    htmlTable()
list(
    feols(src_topic == "Business" ~ cfscore, data = sources),
    feols(src_topic == "Environment" ~ cfscore, data = sources),
    feols(src_topic == "Policy" ~ cfscore, data = sources)
) %>%
    etable() %>%
    htmlTable()
etable(feols(cfscore ~ src_topic, data = sources))
```


# Non policy articles cite fewer ideological sources

```{r, results='asis'}
all.sources$cfscore_std <- all.sources$cfscore - mean(all.sources$cfscore, na.rm = T)
all.sources.balance <- all.sources %>% calculate_balance(types = c("cfscore", "org_category"))
models <-
    list(
        feols(n_left ~ policy_label_gpt, data = all.sources.balance),
        feols(n_right ~ policy_label_gpt, data = all.sources.balance)
    )
etable(models) %>% htmlTable()
```

# Appendix/Supplementary

# NYT comment counts
```{r}
nyt.articles <- articles.b %>% filter(source == "New York Times")
nyt.articles %>% ggplot(aes(x = date, y = n_comments, color = cfscore)) +
    geom_point(alpha = 0.3, size = 10) +
    scale_color_gradient(low = "blue", high = "red")
nyt.articles %>% ggplot(aes(x = date, y = n_comments, color = balance)) +
    geom_point()
```

```{r}
hist(nyt.articles$n_comments)
sd(nyt.articles$n_comments, na.rm = T)
table(nyt.articles$n_comments %>% is.na())
```

```{r}
nyt.articles %>% ggplot(aes(x = cfscore, y = n_comments)) +
    geom_point() +
    geom_smooth() +
    theme_bw()
ggsave(here("paper/figures/nyt-comments-slant-scatter.png"), width = 6, height = 5)
summary(feols(n_comments ~ cfscore, data = nyt.articles))
```

```{r}
m <- feols(n_comments ~ elite_undergrad_ivyplus + age_est_2017 + race.nonwhite + gender + field.journo + edu.has_postgrad, data = nyt.articles)
etable(m) %>% htmlTable()
```


## What articles get more comments?
```{r}
# Journalist characteristics = journalist background is sort of significant I guess?
summary(feols(log(n_comments) ~ elite_undergrad_ivyplus + age_est_2017 + race.nonwhite + gender + field.journo + edu.has_postgrad, data = nyt.articles))

# More comments for more rightward leaning articles.. that's basically it
# Not sure exactly how to interpret this...
summary(feols(n_comments ~ balance, data = nyt.articles))
summary(feols(n_comments ~ cfscore + balance, data = nyt.articles))
summary(feols(log(n_comments) ~ cfscore + balance, data = nyt.articles))

# Interesting...
summary(feols(n_comments ~ cfscore + balance + n, data = nyt.articles))
summary(feols(log(n_comments) ~ cfscore + balance + n, data = nyt.articles))
summary(feols(n_comments ~ cfscore + balance + post2016, data = nyt.articles))

# no super intersting interaction with the post
summary(feols(n_comments ~ (cfscore > 0) * post2016, data = nyt.articles))
summary(feols(log(n_comments) ~ (cfscore > 0) * post2016, data = nyt.articles))

nyt.articles %>% ggplot(aes(x = date, y = n_comments, color = balance)) +
    geom_smooth(se = F, method = "lm") +
    geom_point()
nyt.articles %>% ggplot(aes(x = date, y = n_comments, color = cfscore > 0)) +
    geom_smooth(se = F, method = "lm") +
    geom_point()

etable(
    list(
        feols(n_comments ~ elite_undergrad_ivyplus + age_est_2017 + race.nonwhite + gender + field.journo + edu.has_postgrad, data = nyt.articles),
        feols(n_comments ~ cfscore + balance + n, data = nyt.articles)
    )
)
```

