---
title: "Journalists"
output:
    html_document:
        toc: true
---

```{r include=F}
source(here::here("code/analysis/load.R"))
df <- sources %>%
    calculate_balance(
        types = c("org_category", "cfscore"),
    )
```

# Journalists are Independent of Outlets

```{r}
# Select articles written by journalists with at least 2 articles
df.j <- df %>%
    left_join(authors %>% select(author_name, n) %>% rename(n_articles = n)) %>%
    filter(n_articles > 2, !is.na(author_name))
df.j$author_name %>%
    unique() %>%
    length()
# 708 unique authors
etable(
    feols(balance ~ source, data = df.j),
    feols(balance ~ 1 | author_name, data = df.j),
    feols(balance ~ source | author_name, data = df.j)
) %>% htmlTable()
```


## SD of balance lower in journalists than outlets

```{r}
osds <- df.j %>%
    group_by(source) %>%
    summarize(
        balance_sd = sd(balance, na.rm = T),
        n_articles = n()
    )
osds$balance_sd %>% mean()

sds <- df.j %>%
    group_by(author_name) %>%
    summarize(
        balance_sd = sd(balance, na.rm = T),
        n_articles = n()
    )
sds$balance_sd %>% mean(na.rm = T)
```

## Movers Only
```{r}
df.m <- df.j %>%
    group_by(author_name) %>%
    mutate(n_newspapers = length(unique(source))) %>%
    filter(n_newspapers > 1)
# 98 authors but ok
df.m$author_name %>%
    unique() %>%
    length()
etable(
    feols(balance ~ source, data = df.m),
    feols(balance ~ 1 | author_name, data = df.m),
    feols(balance ~ source | author_name, data = df.m)
) %>% htmlTable()
```

```{r include=F}
etable(
    feols(balance ~ source, data = df.j),
    feols(balance ~ 1 | author_name, data = df.j),
    feols(balance ~ source | author_name, data = df.j),
    tex=T
) %>% writeLines(here('paper/tables/switchers.tex'))
```

## Takeaways

- Within journalist characteristics matter more than outlet for determining balance, with the exception of USA Today weirdly enough

# Journalist Demographics Correlate with Balance

```{r}
df.rn <- sources %>%
    calculate_balance(
        types = c("org_category", "cfscore"),
        articles_df = articles
    )
yvars <- c("n", "balance", "cfscore.sd", "cfscore.median")
models <- c(
    make_models(df.rn, yvars)
)
etable(models, fitstat = c("n")) %>% htmlTable()
```

```{r include=F}
etable(models, fitstat = c("n"), tex=T) %>% writeLines(here('paper/tables/main-journalist-demo.tex'))
```

## Robust to varying specifications

Plot coefficients for a set of different regression specifications:

1. Main specification (Newspaper fixed effects, Impute journalist education)
2. Newspaper fixed effects, No journalist education imputation
3. No newspaper fixed effects, journalist education imputation
4. No newspaper fixed effects, no journalist education imputation

```{r}
models <- list(
    make_models(df.rn, yvars),
    make_models(df, yvars),
    make_models(df.rn, yvars, festring = "| year"),
    make_models(df, yvars, festring = "| year")
)
cplots <- lapply(1:length(yvars), \(i) {
    ymods <- lapply(models, \(m) m[[i]])
    ggcoefplot(ymods)
})
ggarrange(plotlist = cplots, common.legend = T, legend = "bottom")
ggsave(here('paper/figures/coefplot-robust-1.png'), width=7, height=7)
```

## Robust to varying cfscore thresholds

Plot balance effects for different thresholds of cfscore variation
```{r}
models <- lapply(seq(0.1, 0.5, 0.1), \(t) {
    df.t <- sources %>%
        calculate_balance(
            types = c("org_category", "cfscore"),
            thresh = t,
        )
    make_models(df.t, c("balance"))
})
ggcoefplot(models)
ggsave(here('paper/figures/coefplot-robust-2.png'), width=6, height=4)
```

Plot effects for different thresholds of imputation strategy 

1. Main specification
2. Impute all (No DIME scores)
3. Impute off (Only DIME scores)

```{r}
models <- list(
    list(pols = F, impute.all = F, impute.off = F, nwd.sd.thresh = 0.8),
    list(pols = F, impute.all = T, impute.off = F, nwd.sd.thresh = 0.8),
    list(pols = F, impute.all = F, impute.off = T, nwd.sd.thresh = 0.8)
) %>% lapply(\(c) {
    df.t <- sources %>%
        calculate_balance(
            types = c("org_category", "cfscore"),
            cfscore.options = c,
        )
    make_models(df.t, c("balance", "cfscore.sd", "cfscore.median"))
})
cplots <- lapply(1:3, \(i) {
    ymods <- lapply(models, \(m) m[[i]])
    ggcoefplot(ymods)
})
ggarrange(plotlist = cplots, common.legend = T, legend = "bottom")
ggsave(here('paper/figures/coefplot-robust-3.png'), width=7, height=7)
```

## Robust to varying age specification

```{r}
models <- seq(25, 50) %>% lapply(\(age) {
    make_models(df, yvars, j_covars(age))
})
cplots <- lapply(1:4, \(i) {
    ymods <- lapply(models, \(m) tidy(m[[i]]))
    ymods %>%
        bind_rows() %>%
        filter(str_detect(term, "age_est_2017")) %>%
        mutate(age = str_remove(term, "age_est_2017 > ") %>% str_remove("TRUE")) %>%
        ggplot(aes(x = as.numeric(age), y = estimate, ymax = 1.96 * std.error + estimate, ymin = estimate - 1.96 * std.error, color = p.value < 0.05)) +
        geom_hline(yintercept = 0, lty = 2) +
        geom_errorbar(width = 0) +
        geom_point() +
        labs(title = yvars[[i]], x = "Age Threshold") +
        theme_min
})
ggarrange(plotlist = cplots, common.legend = T, legend = "bottom")
ggsave(here('paper/figures/coefplot-robust-4.png'), width=7, height=7)
```

# How much does demographic shift contribute to chanes in balance?

## Cohort effect
```{r}
cohort <- df %>%
    group_by(author_name) %>%
    summarize(
        cohort = year(min(as.Date(date), na.rm = T))
    )
cohort$cohort %>% table(useNA = "ifany")
df.c <- df %>% left_join(cohort)
# Linear specification
feols(balance ~ cohort, data = df.c)
feols(balance ~ cohort > 2016, data=df.c)
# Fixed effect specification
ggcoefplot(feols(balance ~ as.factor(cohort), data = df.c))

ggsave(here('paper/figures/cohort-plot.png'), width=6, height=4)
```

```{r comment=NA} 
etable(
    feols(balance ~ as.factor(cohort), data=df.c), 
    feols(balance ~ cohort > 2016, data=df.c), 
tex=T) %>% writeLines(here('paper/tables/cohort.tex'))
```

- There doesn't seem to be a super strong cohort effect. 
- Evidence against the replacement theory

## Demographic Differences over Time
```{r}
# Age
ggarrange(plotlist = list(
    df %>%
        filter(!is.na(age_est)) %>%
        ggplot(aes(x = date, y = as.numeric(balance), color = age_est_2017 > 37)) +
        geom_smooth(method = "loess") +
        theme_min,
    # Edu
    df %>%
        filter(!is.na(elite_undergrad_ivyplus)) %>%
        ggplot(aes(x = date, y = as.numeric(balance), color = elite_undergrad_ivyplus)) +
        geom_smooth(method = "loess") +
        theme_min,
    # Race
    df %>%
        filter(!is.na(race.nonwhite)) %>%
        ggplot(aes(x = date, y = as.numeric(balance), color = race.nonwhite)) +
        geom_smooth(method = "loess") +
        theme_min
), nrow = 1, legend = "bottom")
```


# Diff in Diff

```{r}
df.an <- df %>%
    filter(year > 2016) %>%
    group_by(author_name) %>%
    summarize(balance_rate = sum(balance, na.rm = T) / sum(!is.na(balance))) %>%
    filter(!is.na(balance_rate))
df.a <- df %>%
    left_join(df.an) %>%
    mutate(
        treat = balance_rate < 0.3,
    )
# Raw trends
df.a %>%
    filter(!is.na(treat)) %>%
    ggplot(aes(x = date, y = as.numeric(balance), color = treat)) +
    geom_vline(xintercept = as.Date("2016-01-01"), lty = 2) +
    geom_smooth(method = "loess") +
    theme_min
ggsave(here('paper/figures/did-raw-trends.png'), width=6, height=4)

df.a %>%
    filter(!is.na(treat)) %>%
    ggplot(aes(x = date, y = as.numeric(balance), color = as.factor(round(balance_rate, digits = 1)))) +
    geom_vline(xintercept = as.Date("2016-01-01"), lty = 2) +
    geom_smooth(method = "loess", se = F) +
    theme_min

make_did_model <- function(df, thresh = 0.3) {
    df.an <- df %>%
        filter(year > 2016) %>%
        group_by(author_name) %>%
        summarize(balance_rate = sum(balance, na.rm = T) / sum(!is.na(balance))) %>%
        filter(!is.na(balance_rate))
    df.a <- df %>%
        left_join(df.an) %>%
        mutate(
            treat = balance_rate < thresh
        )
    feols(balance ~ i(year, treat, ref = 2016) | year + author_name, df.a)
}
models <- lapply(seq(0.2, 0.5, 0.1), \(t) make_did_model(df, t))
ggiplot(models[[2]])
ggsave(here('paper/figures/did-event-study.png'), width=6, height=4)
etable(models[[2]], tex=T) %>% writeLines(here('paper/tables/did.tex'))
```


## Robust to different thresholds
```{r}
ggiplot(models)
ggsave(here('paper/figures/did-event-study-robust.png'), width=6, height=4)
```

## Demographics of the treated group

This aligns with our cross sectional analysis

```{r}
etable(feols(make_fmla("treat"), data = df.a))
etable(feols(make_fmla("treat"), data = df.a), tex=T) %>%
    writeLines(here('paper/tables/treat-demo.tex'))
```

## Demographic regression before and after 2016

```{r}
df.p <- df.a %>%
    filter(!is.na(balance_rate))
interactions <- sapply(j_covars(), \(j) sprintf("%s * post2016", j))
etable(
    feols(make_fmla("balance", interactions, festring = ""), data = df.p),
    feols(make_fmla("balance", interactions, festring = "| source"), data = df.p),
    feols(make_fmla("balance", interactions, festring = "| author_name"), data = df.p)
)
```

Interactions here do not necessarily show that much.
